% Chapter 1

\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1} 

\lhead{Chapter 1. \emph{Introduction}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
Every person in his life at least once leaves his home city for any reason, whether it is a business trip or just a vacation. Taking into account that modern technologies nowadays allow people to move from one point to another in a few hours, such trips becomes much easier to perform. Moreover it gives an opportunity to investigate almost every point on the globe. 

That is why maps become indispensable attribute of any trip. There are two main categories of maps: paper and electronic maps. Classical paper maps can help in any situation but in comparison with electronic map they have one big disadvantage – they are not interactive. Electronic maps in its turn are also separated on "online" and "offline" maps. "Online" maps are interactive, fast and usually not limited to one city. Furthermore there is more than one "online" map, so user can use any on his taste. 

But what to do if for any reason there is no internet connection? For this case "offline" maps can be used, especially if person appears in unknown city. And the main problem of any map that covers large area in this case can be absence of any important information like presence of grocery store or bakery or laundry for small cities. That is why implementation of maps for small areas and cities is very important, because it contains specific information about this particular region.

So the goal of our project was implementation of the map for city Le Creusot with basic set of data and functions like finding way between two points or showing main public facilities. It can be useful for any person whether it's a tourist, visitor on a business trip or a student. Especially we hope that this map can be useful for next \textit{ViBOT/MsCV} promotions for simplifying their life in Le Creusot.
